Analysis for Case 1 (generics)

### 2018-03-22 analysis/case1-generics.Rmd
analysis and cached results for parameter comparison: prev only vs. joint inference"

# Experiment 1:a: Generic endorsements

@@

d.gen.endorse.bayes.prev <- left_join(
  d.gen.endorse.bayes, 
  d.prev.summary %>% 
    rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper) %>%
    select(-n, -empirical_mean)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))

generics.endorsement.spectrum <- ggplot(
    d.gen.endorse.bayes.prev, 
    aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
  )+
  geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
  geom_linerange(position = position_dodge(), size = 1)+
  coord_flip()+
  ylab("Human generic endorsement")+
  xlab("")+
  scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
  scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
  guides(color = guide_colorbar(title = 'Prevalence',
                               ticks = F))+
  theme(legend.position = 'bottom')
```

@@

save(d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes,
     file = "../paper/cached_results/case1_endorseSummary_byItem.RData")

@@

save(d.gen.endorse.regression.prevalence, 
     d.gen.endorse.regression.prevalence.cuevalidity, 
     d.gen.endorse.regression, file = "../paper/cached_results/case1_regressionResults.RData")

@@

var statePrior = Infer({model: function(){
  var component = flip(mixture);
  return component ?
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta(priorParams), b) + Number.EPSILON
      }, bins )
    }) :
    categorical({
      vs: bins,
      ps: map(function(b) {
        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
      }, bins )
    })
}});
'
```

```{r rsaInterpretationModels}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "rejection", samples: 20000, burn:5000, verbose: T})}
'

@@

@@

n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20

model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
# m.samp <- data.frame()
#m.samp.fixed <- data.frame()
#for (i in seq(1, n_chains)){
  #mi.gen <- fread(paste(project.path,  "models/generics/results/", model_prefix, "generic-",
  #                  n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  #m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
# }
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

@@

load(file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# load(file = paste(project.path,  "models/generics/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

@@

```{r gen-prev-forward, eval=F}
#Forward sample Target Prevalence from posterior on parameters (joint inference model)
m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    #filter(type == "withinKind") %>%
    mutate(parameter = paste(param, property, category, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type) %>%
    #mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category"), sep= "_")

m.samp.prevalence <- m.samp.prev.params %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()
```

@@

generics.endorsement.models <- ggplot(d.gen.endorse.rsa.regression, 
                                      aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  #theme(legend.position = "bottom")+
  guides(fill = F)
```

@@

m.gen.fullmodel.prior.parameters <- m.samp %>%
  filter(type == "prior", property %in% example.generics.properties) %>%
  group_by(param, property, category) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
  ungroup() %>%
  select(param, property, category, MAP) %>%
  mutate(param = paste(param, category, sep = "_")) %>%
  select(-category) %>%
  spread(param, MAP) %>%
  rename(mix = mixture_NA, 
         stable_mean = stableFreq_mean, 
         stable_concentration = stableFreq_sampleSize) %>%
  mutate( a = stable_mean * stable_concentration, 
          b = (1 - stable_mean) * stable_concentration)

@@

# run interpreter model to generate "hypothetical intepretation" plots
for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
                                                   b = priorParams[["b"]]),
                               mix = priorParams[["mix"]]), 
                  utt = "generic")
 l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
   )
}

@@

save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
     generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
     file = "../paper/cached_results/case1_modelPosteriors.RData")

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 4, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

@@

```{r generic-endorsement-priors-model-run, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 1000
lg = 0
example.generics.prior.properties <- c(
  "dont eat people", "have beautiful feathers",
  "have wings", "are red",
  "carry malaria", "lay eggs", 
  "are female", "have spots"
  )

for (p in example.generics.prior.properties ) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

@@

    m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
      group_by(Iteration, Chain) %>%
      spread(Parameter, value) %>%
      rowwise() %>%
      mutate(
        a = g*d,
        b = (1-g)*d,
        isPresent = rbinom(1, 1, prob = phi),
        prevalence = ifelse(isPresent == 1, 
                           rbeta(n = 1, 
                                 shape1 = a,
                                 shape2 = b),
                           rbeta(n = 1,
                                 shape1 = 1,
                                 shape2 = 100)),
        Property = p, src = "Structured"
      ) %>% ungroup()

    m.gen.endorse.priors.unstructured <- webppl(
      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

@@

}
save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

@@

```{r generic-endorsement-priors-figure2, eval = F}
ggplot(m.gen.endorse.priors.summary %>% filter(Parameter == 'phi') %>%
         mutate(Property = factor(Property, levels = Property[order(MAP)]) ),
       aes( x = Property, y = MAP, ymin = cred_lower, ymax = cred_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("MAP estimate and 95% HDI of Mixture parameter")
```

>>>>

# Experiment 1a: Generic endorsements

@@

d.gen.endorse.bayes.prev <- left_join(
  d.gen.endorse.bayes, 
  d.prev.summary %>% 
    rename(sentence = item, prev = mean, prev_low = ci_lower, prev_high = ci_upper) %>%
    select(-n, -empirical_stat)
) %>%
  mutate(sentence = factor(sentence, levels = sentence[order(MAP_h)]))

# generics.endorsement.spectrum <- ggplot(
#     d.gen.endorse.bayes.prev, 
#     aes(x = sentence, y = MAP_h - 0.5, ymin = low - 0.5, ymax = high - 0.5, fill = prev)
#   )+
#   geom_bar(stat = 'identity', position = position_dodge(), color='black',  alpha = 1)+
#   geom_linerange(position = position_dodge(), size = 1)+
#   coord_flip()+
#   ylab("Human generic endorsement")+
#   xlab("")+
#   scale_fill_viridis(breaks = c(0, 1), limits = c(0, 1))+
#   scale_y_continuous(limits = c(-0.5,0.5), breaks = c(-0.5, 0, 0.5), labels = c(0, 0.5, 1))+
#   guides(color = guide_colorbar(title = 'Prevalence',
#                                ticks = F))+
#   theme(legend.position = 'bottom')
```

@@

# save(d.gen.endorse.bayes.prev, d.gen.endorse.manipulation.check.bayes,
#      file = "../paper/cached_results/case1_endorseSummary_byItem.RData")

@@

# save(d.gen.endorse.regression.prevalence, 
#      d.gen.endorse.regression.prevalence.cuevalidity, 
#      d.gen.endorse.regression, file = "../paper/cached_results/case1_regressionResults.RData")
load("../paper/cached_results/case1_regressionResults.RData")

@@

// var statePrior = Infer({model: function(){
//  var component = flip(mixture);
//  return component ?
//    categorical({
//      vs: bins,
//      ps: map(function(b) {
//        return probability(Beta(priorParams), b) + Number.EPSILON
//      }, bins )
//    }) :
//    categorical({
//      vs: bins,
//      ps: map(function(b) {
//        return probability(Beta({a:1,b:50}), b) + Number.EPSILON
//      }, bins )
//    })
// }});
'
```

```{r rsaInterpretationModels}
no.utterance.model <- '
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = sample(Beta( flip(mixture) ? priorParams : {a:1,b:100}))
    return { state }
 }, method: "forward", samples: 20000, verbose: T})}
'

no.utterance.model.3comp <- '
var componentParams = [
  {a: 1, b:100},
  {a: priorParams.a1, b:priorParams.b1},
  {a: priorParams.a2, b:priorParams.b2}
]
display(data.prior.mix)
var noUtteranceInterpreter = function() {
  Infer({model: function(){
   var state = beta(componentParams[discrete(data.prior.mix)])
    return {
      state: state, 
  }
  }, method: "forward", samples: 20000, verbose: T})}
'

@@

uncertain.threshold.model.3comp <- '
var componentParams = [
  {a: 1, b:100},
  {a: priorParams.a1, b:priorParams.b1},
  {a: priorParams.a2, b:priorParams.b2}
]
display(data.prior.mix)
display(JSON.stringify(componentParams))
var uncertainThresholdInterpreter = function() {
  Infer({model: function(){
  var component = discrete(data.prior.mix)
  // display(component)
  // display(JSON.stringify(componentParams[component]))
   var state = beta(componentParams[component])
    factor( Math.log(state) )
    return {
      state: state, 
  }
  }, method: "rejection", samples: 20000, verbose: T})}
'

@@

n_chains <- 2
n_samples <- 60000
burn <- n_samples / 2
lg <- 10

#model_prefix <- "results-generics-jointModel-S1-smntcs_"
#fixed_model_prefix <- "results-generics-jointModel-wNoise-inferFixedThresholdCts-20bins-S1-smntcs_some-"
model_prefix <- "results-generics-jointModel-S1-smntcs_generic-3compPriors-2compRef-"
m.samp <- data.frame()
#m.samp.fixed <- data.frame()
for (i in seq(1, n_chains)){
  mi.gen <- read_csv(paste(project.path,  "models/generics/results/", model_prefix,
                           n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  m.samp <- bind_rows(m.samp, mi.gen %>% mutate(chain = i))

#   mi.fixed <- fread(paste(project.path,  "models/generics/results/", fixed_model_prefix,
#                     n_samples, "_burn", burn, "_lag", lg ,"_chain", i, ".csv", sep = ""))
#   m.samp.fixed <- bind_rows(m.samp.fixed, mi.fixed %>% mutate(chain = i))
}
# 
# save(m.samp,
#      file = paste(project.path,  "models/generics/results/", model_prefix, "generic-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
#

@@

## MODEL RESULTS
load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))

@@

```{r gen-prev-forward, eval=F}
#Forward sample Target Prevalence from posterior on parameters (joint inference model)
m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    #filter(type == "withinKind") %>%
    #mutate(parameter = paste(param, property, category, sep = "_")) %>%
    mutate(parameter = paste(param, property, category, component, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type, -component) %>%
    #mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category", "component"), sep= "_")

m.samp.prevalence <- m.samp.prev.params %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()

m.samp.prevalence <- m.samp.prev.params %>%
    mutate(parameter = paste(parameter, component, sep = "_")) %>%
    select(-component) %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate( 
      component = rbinom(n = 1, size = 1, p = mix_1),
      a = ifelse(component == 1, mean_1*sampleSize_1,mean_2*sampleSize_2),
      b = ifelse(component == 1, (1-mean_1)*sampleSize_1, (1-mean_1)*sampleSize_2),
      prevalence = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()

m.samp.prevalence %>% filter(property %in% c("are female", "lay eggs"),
                             category == "Robins") %>%
  ggplot(., aes( x= prevalence))+
  geom_histogram()+
  facet_wrap(~property)
```

@@

generics.endorsement.models <- ggplot(d.gen.endorse.rsa.regression, 
                                      aes ( x = prediction_mean, xmin = prediction_ci_lower, xmax = prediction_ci_upper,
                  y = MAP_h, ymin = low, ymax = high, fill = prev_mean ))+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  geom_linerange(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_point(shape = 21, size = 3)+
  scale_x_continuous(limits = c(-0.01, 1.01), breaks = c(0,  1))+
  scale_y_continuous(limits = c(-0.01, 1.01), breaks = c(0, 1))+
  #scale_fill_continuous(low = "#2b83ba", high = "#d7191c")+
  coord_fixed()+
  xlab("Model prediction")+
  ylab("Human generic endorsement")+
  facet_wrap(~src, nrow = 2)+
  #theme(legend.position = "bottom")+
  guides(fill = F)
generics.endorsement.models
```

@@

# m.gen.fullmodel.prior.parameters <- m.samp %>%
#   filter(type == "prior", property %in% example.generics.properties) %>%
#   group_by(param, property, category) %>%
#   summarize(MAP = estimate_mode(val),
#             cred_upper = hdi_upper(val),
#             cred_lower = hdi_lower(val))

m.gen.fullmodel.prior.parameters <- m.samp %>%
  filter(type == "prior", property %in% example.generics.properties) %>%
  group_by(param, property, category, component) %>%
  summarize(expval = mean(val),
            MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

@@

# m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
#   ungroup() %>%
#   select(param, property, category, MAP) %>%
#   mutate(param = paste(param, category, sep = "_")) %>%
#   select(-category) %>%
#   spread(param, MAP) %>%
#   rename(mix = mixture_NA, 
#          stable_mean = stableFreq_mean, 
#          stable_concentration = stableFreq_sampleSize) %>%
#   mutate( a = stable_mean * stable_concentration, 
#           b = (1 - stable_mean) * stable_concentration)

m.gen.fullmodel.prior.parameters.tidy <- m.gen.fullmodel.prior.parameters %>%
  ungroup() %>%
  mutate(param = paste(param, component, sep = "_")) %>%
  select(param, property, category, expval) %>%
  mutate(param = paste(param, category, sep = "_")) %>%
  select(-category) %>%
  spread(param, expval) %>%
  rename(mixture_0 = mixture_0_NA, 
         mixture_1 = mixture_1_NA, 
         mixture_2 = mixture_2_NA, 
         stable_mean_1 = stableFreq_1_mean, 
         stable_concentration_1 = stableFreq_1_sampleSize,
         stable_mean_2 = stableFreq_2_mean, 
         stable_concentration_2 = stableFreq_2_sampleSize
         ) %>%
  mutate( 
    a_1 = stable_mean_1 * stable_concentration_1, 
    b_1 = (1 - stable_mean_1) * stable_concentration_1,
    a_2 = stable_mean_2 * stable_concentration_2, 
    b_2 = (1 - stable_mean_2) * stable_concentration_2
    )

@@

# run interpreter model to generate "hypothetical intepretation" plots
for (p in example.generics.properties){
 priorParams <- m.gen.fullmodel.prior.parameters.tidy %>% filter(property == p) 
 # inputData = list(prior = list(params = data.frame(a = priorParams[["a"]],
 #                                                   b = priorParams[["b"]]),
 #                               mix = priorParams[["mix"]]), 
 #                  utt = "generic")
  inputData = list(prior = list(params = data.frame(a1 = priorParams[["a_1"]],
                                                   b1 = priorParams[["b_1"]],
                                a2 = priorParams[["a_2"]],
                                                   b2 = priorParams[["b_2"]]),
                               mix = c(priorParams[["mixture_0"]],
                                       priorParams[["mixture_1"]],
                                       priorParams[["mixture_2"]])), 
                  utt = "generic")

 l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model.3comp, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model.3comp, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")

# l0.rs.posterior <- webppl(paste(rsaHelpers, uncertain.threshold.model, uncertain.threshold.call, sep = '\n'), data = inputData, data_var = "data")
 #l0.rs.prior <- webppl(paste(rsaHelpers, no.utterance.model, no.utterance.call, sep = '\n'), data = inputData, data_var = "data")
 gen.listener.predictions <- bind_rows(
   gen.listener.predictions, 
   l0.rs.prior %>% select(value) %>% mutate(property = p, Parameter = "state_Prior"),
    l0.rs.posterior %>% select(value) %>% mutate(property = p, Parameter = "state_Posterior")
   )
}

@@

# save(d.gen.endorse.rsa.regression, gen.inset.distributions.refactored, 
#      generics.fixed.noise.posterior, fixed.threshold.posterior,fixed.threshold.s1opt,uncertain.threshold.s1opt,
#      file = "../paper/cached_results/case1_modelPosteriors.RData")

generics.endorsement.insets <- ggplot(gen.inset.distributions.refactored, 
                                      aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels,
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#2b83ba")+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

generics.endorsement.insets
```

```{r}
for (p in example.generics.properties){
gen.inset.distributions.refactored %>%
    filter(property == p) %>%

    ggplot(. , aes( x = value, fill = Parameter, 
                 color = Parameter, lty = Parameter, alpha = Parameter ))+
  geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
  theme_black()+
  facet_wrap(~property, nrow = 1)+
  geom_label_repel(data = category.text.labels %>%
                     filter(property ==p),
                  aes(label = category, x = x , y = y),
                  inherit.aes = F, color = "#b2df8a", fill='black')+
    #scale_fill_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    #scale_color_manual(values = c("#636363", "#abdda4", "#2b83ba", "#d7191c"))+
    scale_fill_manual(values = c("white", "#fb9a99", "#b2df8a"))+
    scale_color_manual(values = c("white", "#fb9a99", "#b2df8a"))+
    scale_alpha_manual(values = c(0.8, 0.5, 0))+
    #scale_linetype_manual(values = c(3, 4, 2, 1))+
    scale_linetype_manual(values = c(3, 4, 1))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    xlab("Prevalence") +
    ylab("Scaled density")+
    theme(legend.position = "bottom", legend.title = element_blank())
  ggsave(paste(
    "~/Documents/research/talks/generics/mit-bcs-2018-03/figs/generics-insets-",
    p, ".pdf", sep = ""), width = 2.5, height = 2.5)
}

@@

```{r testingNewViz}

d.prev.zeros <- d.prev %>%
  mutate(nonZero = prevalence > 0) %>%
  group_by(Property) %>%
  tidyboot_mean(column = nonZero)

d.prev.zeros %>% 
  mutate(Property = factor(Property, levels = Property ))
  ggplot(., aes( x = Property, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_col()

ggplot(d.prev %>%
         filter(prevalence > 0), 
           aes( x = prevalence))+
           #aes( x = prevalence, color = src, lty = src))+
    geom_density(aes(y = ..scaled..), adjust = 0.5, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #stat_ecdf(size = 1)+
    #scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    #scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property)+
    #scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 100), limits= c(0, 100))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("") +
    ylab("Normalized probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())
```

```{r generic-endorsement-priors-model-run, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 20000
lg = 0
# example.generics.prior.properties <- c(
#   "dont eat people", "have beautiful feathers",
#   "have wings", "are red",
#   "carry malaria", "lay eggs", 
#   "are female", "have spots"
#   )

for (p in levels(d.gen.endorse.priors$Property)) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

@@

        # m.gen.endorse.priors.structured.predictive <- m.gen.endorse.priors.structured %>%
    #   group_by(Iteration, Chain) %>%
    #   spread(Parameter, value) %>%
    #   rowwise() %>%
    #   mutate(
    #     a = g*d,
    #     b = (1-g)*d,
    #     isPresent = rbinom(1, 1, prob = phi),
    #     prevalence = ifelse(isPresent == 1, 
    #                        rbeta(n = 1, 
    #                              shape1 = a,
    #                              shape2 = b),
    #                        rbeta(n = 1,
    #                              shape1 = 1,
    #                              shape2 = 100)),
    #     Property = p, src = "Structured"
    #   ) %>% ungroup()
    # 
    m.gen.endorse.priors.unstructured <- webppl(
      paste(genericEndorsementPriorModelHelpers, unstructuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))

@@

}
# save(m.gen.endorse.priors.posteriorPredictive, file = '../analysis/generics-priors-posteriorPredictives.Rdata')

@@

## Appendix C: Comparison of prior parameters inferred using only prior data and in joint-inference model
```{r generic-priors-parameters, eval = F}
m.gen.endorse.priors.posteriorPredictive <- data.frame()
n_samples <- 20000
lg = 0
# example.generics.prior.properties <- c(
#   "dont eat people", "have beautiful feathers",
#   "have wings", "are red",
#   "carry malaria", "lay eggs", 
#   "are female", "have spots"
#   )

m.gen.endorse.priors.parameters <- data.frame()
for (p in levels(d.gen.endorse.priors$Property)) {
  priorData <- filter(d.gen.endorse.priors, Property == p)$prevalence

    m.gen.endorse.priors.structured <- webppl(
      paste(genericEndorsementPriorModelHelpers, structuredPriorModel, sep = ""),
                                 data = priorData, data_var = "data",
                                 model_var = "model",
                                 chains = 2,
                                 cores = 2,
                                 inference_opts =
                                   list(method = "MCMC",
                                        samples = n_samples,
                                        burn = n_samples / 2,
                                        lag = lg,
                                        verbose = T))
m.gen.endorse.priors.structured.summary <- m.gen.endorse.priors.structured %>%
  group_by(Parameter) %>%
  summarize(MAP = estimate_mode(value),
            cred_upper = hdi_upper(value),
            cred_lower = hdi_lower(value))

    m.gen.endorse.priors.parameters <- bind_rows(
      m.gen.endorse.priors.parameters,
      m.gen.endorse.priors.structured.summary %>%
        mutate(Property = p)
      )
}

# save(m.gen.endorse.priors.parameters, file = '../analysis/generics-priors-posteriorParameters.Rdata')
```

```{r}
load(file = paste(project.path,  "models/generics/results/", "results-generics-jointModel-S1-smntcs_generic-100000_burn50000_lag20_3chains.RData", sep = ""))

m.gen.endorse.joint.prior.parameters <- m.samp %>%
  filter(type %in% c("prior", "targetPrevalence")) %>%
  group_by(property, category, type, param) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))
```

```{r}
left_join(
  m.gen.endorse.priors.parameters,
  m.gen.endorse.joint.prior.parameters %>%
    filter(type == "prior") %>%
    rowwise() %>%
    mutate(Parameter = ifelse(param == "mixture", "phi",
                              ifelse(category == "mean", "g", "d"))) %>%
    ungroup() %>% 
    select(property, Parameter, MAP, cred_upper, cred_lower) %>%
    rename(Property = property,
           MAP_joint = MAP,
           cred_upper_joint = cred_upper,
           cred_lower_joint = cred_lower)
) %>%
  mutate(Parameter = factor(Parameter,
                            levels = c("phi", "g", "d"),
                            labels = c(expression(paste("mixture parameter (", phi,")", sep = "")),
                                       expression(paste("stable component: mean (", gamma,")", sep = "")),
                                       expression(paste("stable component: concentration (", xi,")", sep = ""))))) %>%
  ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                 y = MAP_joint, ymin = cred_lower_joint, ymax = cred_upper_joint ))+
  geom_point()+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
  facet_wrap(~Parameter, scales = 'free', labeller = label_parsed)+
  xlab("Inferred values with only prevalence data")+
  ylab("Inferred values in joint-inference model")
```
